---
title: "Clean Gephi Data"
author: "Pierson Cooke"
date: "2023-02-28"
output: html_document
---

```{r warning=FALSE}
library(tidyverse)
library(dplyr)

nodes <- read.csv("/Users/piersoncooke/Desktop/star-wars-network-data-master/Networks-Project/nodes_full.csv")
```

There are a lot of Affiliations with just a single character, which makes it somewhat difficult to visualize in Gephi. Therefore, we chose to group all the Affiliations with less than 4 characters into a group called "Other" because we believe that looking into Affiliations with very few characters won't help much with out analysis.
```{r}

(affiliation_table <- table(nodes$Affiliations))

nodes$Affiliations <- ifelse(nodes$Affiliations %in% 
                               names(affiliation_table[affiliation_table >= 4]), 
                             nodes$Affiliations, "Other")

table(nodes$Affiliations)
```

Similarly, we did the same thing with the locations of each character. We took some steps to clean the data in order to correct any spelling mistakes and to assign one-off locations into another group. The locations column shows where characters spent a majority of their time and we subsequently chose 3 as the cutoff to weed out any locations that didn't have at least 3 characters who spent a majority of time there.
```{r}
(location_table <- table(nodes$Locations))

nodes$Locations[nodes$Locations == "Coruscant / Malastare"] <- "Coruscant"
nodes$Locations[nodes$Locations == "Death Star II"] <- "Death Star"
nodes$Locations[nodes$Locations == "Jabba's Palce"] <- "Jabba's Palace"
nodes$Locations[nodes$Locations == "Kaminon"] <- "Kamino"
nodes$Locations[nodes$Locations == "Kamino"] <- "Kamino"
nodes$Locations[nodes$Locations == "Naboo, Death Star II"] <- "Naboo"

nodes$Locations <- ifelse(nodes$Locations %in% names(location_table[location_table >= 3]), 
                             nodes$Locations, "Other")

table(nodes$Locations)
```

Finally, we replicated the steps above to clean the column indicating which species each character falls under. 
```{r}

nodes$Species.Droids[is.na(nodes$Species.Droids)] <- "Unknown"

nodes$Species.Droids[nodes$Species.Droids == "Human "] <- "Human"

(species_table <- table(nodes$Species.Droids))

nodes$Species.Droids <- ifelse(nodes$Species.Droids %in% 
                               names(species_table[species_table >= 2]), 
                             nodes$Species.Droids, "Other")

table(nodes$Species.Droids)
```

```{r}
write.csv(nodes, "/Users/piersoncooke/Desktop/star-wars-network-data-master/Networks-Project/nodes_cleaned.csv", row.names = FALSE)
```

